Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-26 main.tex
Sort citations by location in text.
Removed uncertainty estimation from parameter table.

\usepackage{amsmath}
\usepackage{booktabs}  % nice tables
\usepackage[margin=25mm]{geometry}
\usepackage[natbib=true,style=numeric]{biblatex}
% NOTE : this file is automatically generated from Zotero, do not edit
% manually!
\addbibresource{references.bib}
\usepackage{siunitx}  % use for all units
\usepackage{subcaption}  % for subfigures
\usepackage[]{todonotes}  % use [disable] to hide notes

@@

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters and estimated uncertainties (standard deviation) for the
balance assist bicycle with and without a rider. These are found using the
measurement approach for geometric and inertial parameters for a bicycle
explained in \citet{Moore2012}. The rider inertial parameters are derived from
the 83.5~\si{\kilogram} rider ``Jason'' available in BicycleParameters
1.1.1~\citep{Moore2024}. The variable names match the notation and definitions
from the benchmark bicycle model presented in
\citet{Meijaard2007}.\todo[inline]{Uncertainties are based on best guess for
uncertainty in the raw measurements, may be better to remove them as they
aren't so meaningful.}
%
\begin{table}[h]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{llrrrr}
    \toprule
    Variable & Unit & Without Rider & Uncertainty & With Rider & Uncertainty \\
    \midrule
    \(c\) & \si{\meter} & 0.04 & 0.01 & 0.04 & 0.01 \\
    \(g\) & \si{\meter\per\second\squared} & 9.80665 & NA & 9.80665 & NA \\
    \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 0.02 & 19.7 & 0.3 \\
    \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & 0.03 & -3.5 & 0.2 \\
    \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 0.08 & 22.7 & 0.4 \\
    \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 0.03 & 5.0 & 0.1 \\
    \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0005 & 0.0995 & 0.0005 \\
    \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.0009 & 0.1902 & 0.0009 \\
    \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.003 & 0.298 & 0.003 \\
    \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & 0.007 & -0.038 & 0.007 \\
    \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.006 & 0.257 & 0.006 \\
    \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.003 & 0.057 & 0.003 \\
    \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.0006 & 0.1023 & 0.0006 \\
    \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.0007 & 0.1887 & 0.0007 \\
    \(\lambda\) & \si{\radian} & 0.25 & 0.03 & 0.25 & 0.03 \\
    \(m_B\) & \si{\kilogram} & 22.50 & 0.01 & 106.00 & 0.01 \\
    \(m_F\) & \si{\kilogram} & 2.23 & 0.01 & 2.23 & 0.01 \\
    \(m_H\) & \si{\kilogram} & 4.30 & 0.01 & 4.30 & 0.01 \\
    \(m_R\) & \si{\kilogram} & 4.08 & 0.01 & 4.08 & 0.01 \\
    \(r_F\) & \si{\meter} & 0.3523 & 0.0001 & 0.3523 & 0.0001 \\
    \(r_R\) & \si{\meter} & 0.3489 & 0.0001 & 0.3489 & 0.0001 \\
    \(w\) & \si{\meter} & 1.113 & 0.008 & 1.113 & 0.008 \\
    \(x_B\) & \si{\meter} & 0.52 & 0.01 & 0.374 & 0.002 \\
    \(x_H\) & \si{\meter} & 0.92 & 0.02 & 0.92 & 0.02 \\
    \(z_B\) & \si{\meter} & -0.52 & 0.02 & -1.009 & 0.003 \\
    \(z_H\) & \si{\meter} & -0.860 & 0.006 & -0.860 & 0.006 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}  % nice tables
\usepackage[margin=25mm]{geometry}
\usepackage[natbib=true,style=numeric,sorting=none]{biblatex}
% NOTE : this file is automatically generated from Zotero, do not edit
% manually!
\addbibresource{references.bib}
\usepackage{siunitx}  % use for all units
\usepackage{subcaption}  % for subfigures
\usepackage[]{todonotes}  % use [disable] to hide notes

@@

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters for the balance assist bicycle with and without a rider.
These are found using the measurement approach for geometric and inertial
parameters for a bicycle explained in \citet{Moore2012}. The rider inertial
parameters are derived from the 83.5~\si{\kilogram} rider ``Jason'' available
in BicycleParameters 1.1.1~\citep{Moore2024}. The variable names match the
notation and definitions from the benchmark bicycle model presented in
\citet{Meijaard2007}.
%
\begin{table}[ht]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{llrr}
    \toprule
    Variable & Unit & Without Rider & With Rider \\
    \midrule
    \(c\) & \si{\meter} & 0.04 & 0.04 \\
    \(g\) & \si{\meter\per\second\squared} & 9.80665 & 9.80665 \\
    \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 19.7 \\
    \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & -3.5 \\
    \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 22.7 \\
    \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 5.0 \\
    \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0995 \\
    \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.1902 \\
    \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.298 \\
    \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & -0.038 \\
    \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.257 \\
    \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.057 \\
    \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.1023 \\
    \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.1887 \\
    \(\lambda\) & \si{\radian} & 0.25 & 0.25 \\
    \(m_B\) & \si{\kilogram} & 22.50 & 106.00 \\
    \(m_F\) & \si{\kilogram} & 2.23 & 2.23 \\
    \(m_H\) & \si{\kilogram} & 4.30 & 4.30 \\
    \(m_R\) & \si{\kilogram} & 4.08 & 4.08 \\
    \(r_F\) & \si{\meter} & 0.3523 & 0.3523 \\
    \(r_R\) & \si{\meter} & 0.3489 & 0.3489 \\
    \(w\) & \si{\meter} & 1.113 & 1.113 \\
    \(x_B\) & \si{\meter} & 0.52 & 0.374 \\
    \(x_H\) & \si{\meter} & 0.92 & 0.92 \\
    \(z_B\) & \si{\meter} & -0.52 & -1.009 \\
    \(z_H\) & \si{\meter} & -0.860 & -0.860 \\
    \bottomrule
  \end{tabular}
\end{table}
